Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-16 paper/paper.Rmd
simplify buffering intro
explicitily mention `rasterLayer` arg

Buffering is mostly applied in the coordinate space due to the scattered appearance of observations in this space.
However, there is no practical limitation that would prevent this method to be applied in a 2D + time setting.
Because \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.

@@

The "Spatial blocking" from package \pkg{blockCV} comes with various options to customize the zone creation.
Besides the choice of relying on an initial random  (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`) for the final partition aggregation, support for SDM specific background data is built-in.
Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
Ultimately, users can also supply a user-defined polygon which defines the zones.

>>>>

Buffering is mostly applied in the coordinate space.
However, there is no practical limitation that would prevent this method to be applied in a 2D + time setting.
Because \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.

@@

The "Spatial blocking" from package \pkg{blockCV} comes with various options to customize the zone creation.
Besides the choice of relying on an initial random  (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`) for the final partition aggregation, support for SDM specific background data is built-in.
Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
Ultimately, users can also supply a user-defined polygon via argument `rasterLayer` to define the zones.
